Verifying Demonstrations

### 2017-08-10 intro.tex

\blockcquote{2016DemonstrationsInSeoul}{%
  For the police, the aim is to measure the maximum crowd occupying a certain 
  space at any given time so that they could determine the size of police 
  personnel and resources to deploy%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  Organizers seek to track the entire flow of people from the protest’s start 
  to its finish. They collect estimates given by counters deployed at different 
  locations to size up the crowds in each area and update the numbers 
  throughout the duration of the protest.%
}

>>>>

The organizers want to count everyone who participated at any time and in any 
of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We thus settle for the following definition.

\begin{definition}[A protest]
  A protest is an event identified by its cause.
\end{definition}
